### 2022-05-08 sections/bdt_Htautau.tex
addressing Luca's comments to V1.4

 \text{min}($m_{jj}$) &   &  $12$               &           & $11$     &       &  &         \\

@@

\item $\chi^2$ of the kinematic fit of the momentum of the invisible decay products of the tau leptons.

@@

\item \text{min}($m_{\tau\tau \text{j}}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavour jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\tau\tau\text{q}}$.
\item \text{min}($m_{\text{jj}}$) is the invariant mass of two light-flavour jets, minimized by choosing different jets, reflects the invariant mass of the $W$ candidate.

@@

\item $E_{\tau\text{i}}/E_{\tau\text{i},\text{fit}}$ (\text{i}=1,2) is the momentum fraction carried by the visible decay products from the leading and subleading tau decays. It is based on the best-fit 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section. For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state.% which is evident in the excess around 1 in Figure \ref{fig:x12_fit}. 

@@

A comparison between data and the predicted background for the leading $\had$ $\pt$  and the visible invariant mass of the di-tau system ($m_{\tau\tau}$)
distributions in SRs and VRs, after applying fake factors, 
%some of these variables in three main decay final states($t_{\ell}\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
are shown in Figure~\ref{fig:taupt_prefit} and~\ref{fig:mtt}, respectively.
%each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_{\ell}hadhad}.
%The comparison between the data and predicted background after preselection for the distributions of two of the most 
%discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit'').
%The expected signals are also shown after scaled up for the shape comparison of the distributions.
%by a large factor normalized to the total number of events in the predicted
%background for the shape comparison.   
%corresponding to $\BR(t\to Hq)=0.2\%$ is also shown.
The last bin of each plot contains the overflow entries.
The bottom panel displays the ratio of data to the background (``Bkg'') prediction as discussed in section~\ref{sec:background_model}.
The hashed area represents the total uncertainty of the background.
A good description of the data by the background model is observed in all cases.
The final observable used to extract the signal contribution is the BDT distribution in each SR corresponding to either $tuH$ or $tcH$ signal.

%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l2tau1bnj_os_log_.pdf} &
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b1j_ss_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_ss_log_.pdf}\\
(a) & (b) & (c) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_os_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b3j_os_log_.pdf} &
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l2tau1bnj_ss_log_.pdf} \\
(d) & (e) & (f)\\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b2jos_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jos_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jss_log_.pdf}\\
(g) & (h) & (i)\\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{Leading $\thad$ $\pt$  distributions obtained before the fit to data (``Pre-Fit'') showing 
  the expected background and $tuH$ signals after applying fake factors in the following: $t_{\ell}\thadhad$ (a),
 $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$-SS  (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j SS (i).
 The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
 %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
 Overflow events are included in the last bin. ``Other MC'' (``Rare'') includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channel. The $tuH$ signal is scaled using a normalization factor of 2 to 50.   
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the data to prediction ratio.}
\label{fig:taupt_prefit}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l2tau1bnj_os_log_mtt.pdf} &
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b1j_ss_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b2j_ss_log_mtt.pdf}\\
(a) & (b) & (c) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b2j_os_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b3j_os_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l2tau1bnj_ss_log_mtt.pdf}\\
(d) & (e) & (f)\\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b2jos_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b3jos_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b3jss_log_mtt.pdf}\\
(g) & (h) & (i)\\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{Visible invariant mass of di-tau system ($m_{\tau\tau}$) distributions obtained before the fit to data (``Pre-Fit'') showing 
  the expected background and $tuH$ signals after applying fake factors in the following: $t_{\ell}\thadhad$ (a),
 $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$-SS (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j SS (i).
 The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
 %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
 Overflow events are included in the last bin. ``Other MC'' (``Rare'') includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channel. The $tuH$ signal is scaled using a normalization factor of 2 to 50.   
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the data to prediction ratio.}
\label{fig:mtt}
\end{figure}

>>>>

 \text{min}($m_{\text{jj}}$) &   &  $12$               &           & $11$     &       &  &         \\

@@

\item $\chi^2$ of the kinematic fit of the momentum of the invisible decay products of the tau leptons as defined in eq.~(\ref{eq:eq1}).

@@

\item \text{min}($m_{\tau\tau \text{j}}$) is the minimum value of the visible mass of the di-tau candidates (include leptonic tau) and the light-flavour jet system, minimized by choosing different jet, reflecting the invariant masss of the visible FCNC top decaying products.
\item \text{min}($m_{\text{jj}}$) is the minimum value of all the invariant mass of all the light-flavour jet pairs, reflecting the invariant mass of the $W$ boson candidate.

@@

\item $E_{\tau\text{i}}/E_{\tau\text{i},\text{fit}}$ (\text{i}=1,2) is the momentum fraction carried by the visible decay products from the leading and subleading tau decays. It is based on the best-fit of the 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section. For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state.% which is evident in the excess around 1 in Figure \ref{fig:x12_fit}. 

@@

A comparison between data and the predicted background for the leading $\had$ $\pt$  and the visible invariant mass of the di-tau system ($m_{\tau\tau}$)
distributions in SRs and VRs, after applying fake factors, 
%some of these variables in three main decay final states($t_{\ell}\hadhad$, $t_h\hadhad$, and $t_h\lephad$)
are shown in Figure~\ref{fig:taupt_prefit} and~\ref{fig:mtt}, respectively.
%each of the SRs considered is shown in Figures~\ref{fig:mva_input_hadhad} -~\ref{fig:mva_input_{\ell}hadhad}.
%The comparison between the data and predicted background after preselection for the distributions of two of the most 
%discriminating BDT input variables in the $\hadhad$ channel before the fit to data (``Pre-Fit'').
%The expected signals are also shown after scaled up for the shape comparison of the distributions.
%by a large factor normalized to the total number of events in the predicted
%background for the shape comparison.   
%corresponding to $\BR(t\to Hq)=0.2\%$ is also shown.
%The last bin of each plot contains the overflow entries.
%The bottom panel displays the ratio of data to the background (``Bkg'') prediction as discussed in section~\ref{sec:background_model}.
%The hashed area represents the total uncertainty of the background.
A good description of the data by the background model is observed in all cases.
The final observable used to extract the signal contribution is the BDT distribution in each SR corresponding to either $tuH$ or $tcH$ signal.

%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l2tau1bnj_os_log_.pdf} &
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b1j_ss_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_ss_log_.pdf}\\
(a) & (b) & (c) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_os_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b3j_os_log_.pdf} &
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l2tau1bnj_ss_log_.pdf} \\
(d) & (e) & (f)\\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b2jos_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jos_log_.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jss_log_.pdf}\\
(g) & (h) & (i)\\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{Leading $\thad$ $\pt$  distributions obtained before the fit to data (``Pre-Fit'') showing 
  the expected background and $tuH$ signals after applying fake factors in the following regions: $t_{\ell}\thadhad$ (a),
 $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$-SS  (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j SS (i).
 The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
 %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
 Overflow events are included in the last bin. ``Other MC'' (``Rare'') includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channel. The $tuH$ signal is scaled using a normalization factor of 2 to 50.   
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the data to prediction ratio.}
\label{fig:taupt_prefit}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l2tau1bnj_os_log_mtt.pdf} &
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b1j_ss_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b2j_ss_log_mtt.pdf}\\
(a) & (b) & (c) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b2j_os_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l1tau1b3j_os_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg1l2tau1bnj_ss_log_mtt.pdf}\\
(d) & (e) & (f)\\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b2jos_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b3jos_log_mtt.pdf}&
\includegraphics[page=1,width=0.28\textwidth]{figures/mtt/tuH_reg2mtau1b3jss_log_mtt.pdf}\\
(g) & (h) & (i)\\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{Visible invariant mass of the di-tau system ($m_{\tau\tau}$) distributions obtained before the fit to data (``Pre-Fit'') showing 
  the expected background and $tuH$ signals after applying fake factors in the following regions: $t_{\ell}\thadhad$ (a),
 $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_{\ell}\thadhad$-SS (f), $t_h\thadhad$-2j (g), $t_h\thadhad$-3j (h) and $t_h\thadhad$-3j SS (i).
 The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
 %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
 Overflow events are included in the last bin. ``Other MC'' (``Rare'') includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channel. The $tuH$ signal is scaled using a normalization factor of 2 to 50.   
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the data to prediction ratio.}
\label{fig:mtt}
\end{figure}

### 2022-05-08 sections/data_presel.tex
addressing Luca's comments to V1.4

Single-electron and single-muon triggers with low $\pt$ thresholds and lepton isolation requirements are combined in a logical OR 
with higher-threshold triggers but with a looser identification criterion and without any isolation requirement.
The lowest $\pt$ threshold used for muons is 20 (26)~\gev\ in 2015 (2016-2018), while for electrons the threshold is 24 (26)~\gev.
%For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
For di-tau triggers, the $\pt$ threshold of the leading (subleading) $\had$ candidate is 35 (25)~\gev.
%Events satisfying the trigger selection are required to have at least one primary vertex candidate.
To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have a \pt of 1~GeV above the threshold. 
The reconstructed taus are required to have a \pt of 5 GeV higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
%The signal final state including a light lepton (electron or muon) or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.
%The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger. Further requirements are defined targeting different signal decay modes:  
The events in the leptonic channel are recorded by a single-electron or single-muon trigger, required to have exactly one electron or muon that matches, within $\Delta R < 0.15$, the lepton reconstructed by at least one of the possible triggers. Further requirements are defined targeting different signal decay modes:  
\begin{itemize}
\item $t_h\lephad$: Targeting into the $t_hH$ and $t_ht(qH)$ final states with a $H\to\lephad$ decay. Exactly one $\had$ with opposite-side charge to $\lep$ is required, including at least three jets with exactly one $b$-jet.
\item $t_{\ell}\hadhad$: Targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay. Exactly one light lepton and two opposite-sign $\had$ are selected, including at least one jet with exactly one $b$-jet.
\item $t_{\ell}\had$: Also targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay where one $\had$ fails the tau reconstruction or identification so that there is only one reconstructed $\had$ candidate.
  To reduce the SM backgrounds and avoid overlaps with the other selections, exactly one $\had$ with same-sign charge to the light lepton is required.
  In addition, at least two jets including exactly one $b$-jet are required.
\end{itemize}

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{Summary of preselection requirements. 
The leading and subleading $\had$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
\begin{center}
\begin{tabular}{c|ccc|c}
\toprule\toprule
\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & \multicolumn{1}{c}{hadronic channel} \\ 
%\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & hadronic channel \\ 
& $t_h\lephad$ & $t_{\ell}\hadhad$ &  $t_{\ell}\had$ & $t_h\hadhad$\\
\midrule
Trigger & \multicolumn{3}{c|}{single-lepton trigger} & di-$\tau$ trigger  \\
Leptons  & \multicolumn{3}{c|}{=1 isolated $e$ or $\mu$}  & =0 isolated $e$ or $\mu$ \\
$\had$  & $=$1 $\had$ & $\geq$2 $\had$ & $=$1 $\had$ & $\geq$2 $\had$ \\
Electric charge ($Q$) & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} < 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} > 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ \\
Jets  &   $\geq$ 3 jets & $\geq$1 jets & $\geq$2 jets & $\geq$3 jets \\
$b$-tagging & \multicolumn{3}{c|}{=1 $b$-jets} & =1 $b$-jets\\
\bottomrule\bottomrule
\end{tabular}
\label{tab:preselection}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

>>>>

Single-electron and single-muon triggers with low $\pt$ thresholds and lepton isolation requirements are combined in a logical OR 
with higher-threshold triggers but with a looser identification criterion and without any isolation requirement.
The lowest $\pt$ threshold used for muons is 20 (26)~\gev\ in 2015 (2016-2018), while for electrons the threshold is 24 (26)~\gev.
%For ditau triggers, the $\pt$ threshold of the leading (trailing) $\tauhad$ candidate is 35 (25)~\gev\ with the medium identification required.
For di-tau triggers, the $\pt$ threshold of the leading (subleading) $\had$ candidate is 35 (25)~\gev.
%Events satisfying the trigger selection are required to have at least one primary vertex candidate.
To reduce the impact of the trigger efficiency uncertainty around the threshold, the leptons are required to have a \pt of 1~GeV above the threshold. 
The reconstructed taus are required to have a \pt of 5 GeV higher than the trigger threshold, and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
%The signal final state including a light lepton (electron or muon) or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.
%The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger. Further requirements are defined targeting different signal decay modes:  
The events in the leptonic channel are recorded by a single-electron or single-muon trigger, required to have exactly one electron or muon that matches, within $\Delta R < 0.15$, the lepton reconstructed by at least one of the possible triggers. Further requirements are defined targeting different signal decay modes:  
\begin{itemize}
\item $t_h\lephad$: Targeting into the $t_hH$ and $t_ht(qH)$ final states with a $H\to\lephad$ decay. Exactly one $\had$ with opposite-side charge to $\lep$ is required, including at least three jets with exactly one $b$-jet.
\item $t_{\ell}\hadhad$: Targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay. Exactly one light lepton and two opposite-sign $\had$ are selected, including at least one jet with exactly one $b$-jet.
\item $t_{\ell}\had$: Also targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with a $H\to\hadhad$ decay where one $\had$ fails the tau reconstruction or identification so that there is only one reconstructed $\had$ candidate.
  To reduce the SM backgrounds and avoid overlaps with the other ATLAS searches, exactly one $\had$ with same-sign charge to the light lepton is required.
  In addition, at least two jets including exactly one $b$-jet are required.
\end{itemize}

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{Summary of preselection requirements. 
The leading and subleading $\had$ candidates are denoted by $\tau_{\mathrm{had1}}$ and $\tau_{\mathrm{had2}}$ respectively.}}
\begin{center}
\begin{tabular}{c|ccc|c}
\toprule\toprule
\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & \multicolumn{1}{c}{hadronic channel} \\ 
%\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & hadronic channel \\ 
& $t_h\lephad$ & $t_{\ell}\hadhad$ &  $t_{\ell}\had$ & $t_h\hadhad$\\
\midrule
Trigger & \multicolumn{3}{c|}{single-lepton trigger} & di-$\tau$ trigger  \\
Leptons  & \multicolumn{3}{c|}{=1 isolated $e$ or $\mu$}  & =0 isolated $e$ or $\mu$ \\
$\had$  & $=$1 $\had$ & $\geq$2 $\had$ & $=$1 $\had$ & $\geq$2 $\had$ \\
Electric charge ($Q$) & $Q_\ell \times Q_{\tau_{\mathrm{had1}}} < 0$ & $Q_{\tau_{\mathrm{had1}}} \times Q_{\tau_{\mathrm{had2}}} < 0$ & $Q_\ell \times Q_{\tau_{\mathrm{had1}}} > 0$ & $Q_{\tau_{\mathrm{had1}}} \times Q_{\tau_{\mathrm{had2}}} < 0$ \\
Jets  &   $\geq$ 3 jets & $\geq$1 jets & $\geq$2 jets & $\geq$3 jets \\
$b$-tagging & \multicolumn{3}{c|}{=1 $b$-jets} & =1 $b$-jets\\
\bottomrule\bottomrule
\end{tabular}
\label{tab:preselection}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%
